Figures

### 2017-03-07 Code_05 Map_Plot.Rmd
Updated Post Analysis Null Test
Added the potential to calculate exponent values for both climate and
area.

Figure 1: A map of the study area, sites and 
```{r Load Data, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, dependson=c(1,2,5)}
#Call necessary packages.
library(rgdal);library(dplyr)

@@

>>>>

Figure 1: A map of the study area, sites and 
```{r Load Data, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE, dependson=c(1,2,5)}
#Call necessary packages.
library(rgdal);library(tidyverse);library(sp);library(maptools)

@@

Here I'm simply creating a sites shapefile with the adjusted size values for the point sizes. These will then be used to inform point sizes in QGIS.
```{r Map Plot, echo=FALSE, message=FALSE, warning=FALSE}
x = c(seq(1,3.5,by = 0.5),max(WS.MetaD$Area.size))
round(((((x/3.5)^(1/0.4))-0.02) * diff(range(WS.MetaD$Area)))+min(WS.MetaD$Area),0)

WS.MetaD = mutate(WS.MetaD, Area.size = ((((Area-min(Area))/(diff(range(Area))))+0.02)^0.4)*3.5)
BCAlbers = CRS("+init=epsg:3005")
sp = SpatialPointsDataFrame(data = WS.MetaD, coords = WS.MetaD[,c("UTM_E","UTM_N")], proj4string = BCAlbers)
writeOGR(sp, dsn = "mapPlot", layer = "sites", driver="ESRI Shapefile", overwrite_layer = T, morphToESRI = T)

```
